---
title: "Exercise_final (Chapter(7-9)"
author: "TerrenceN"
date: "September 21, 2019"
output: html_document
---

## Excercise 7.1

```{r}
plot(x = -3:3, y = 7:13, type = "n", main = "", xlab = "", ylab = "")

abline(h = c(7, 13), col = "blue", lty = 2, lwd = 2)
abline(v = c(-3, 3), col = "blue", lty = 2, lwd = 2)

text(x = 0, y = 10, labels = "somthing\nprofound")

arrows(x0 = -2.5, y0 = 12.5, x1 = -1, y1 = 10.5)
arrows(x0 = -2.5, y0 = 10,   x1 = -1, y1 = 10)
arrows(x0 = -2.5, y0 = 7.5,  x1 = -1, y1 = 9.5)

arrows(x0 = 2.5, y0 = 12.5, x1 = 1, y1 = 10.5)
arrows(x0 = 2.5, y0 = 10,   x1 = 1, y1 = 10)
arrows(x0 = 2.5, y0 = 7.5,  x1 = 1, y1 = 9.5)

terry<- data.frame(
  weight = c(55,85,75,42,93,63,58,75,89,67),
  height = c(161,185,174,154,188,178,170,167,181,178),
  sex = factor(c("Female","Male","Male","Female","Male","Male","Female","Male","Male","Female"))
)

plot(terry$weight, terry$height, type="n",
     xlab="Weights (kg)", ylab="Heights (cm)",
     main="Graph 1 showing Height measured against weight- Sample size -10 people"
)
points(terry$weight[terry$sex == "Male"], terry$height[terry$sex == "Male"],
       pch = 4, col = "red"
)
points(terry$weight[terry$sex == "Female"], terry$height[terry$sex == "Female"],
       pch = 2, col = "black"
)
legend("topleft", legend=c("Male","Female"),
       pch=c(4, 2), col=c("red", "black")
)
```

## Excercise 7.2
```{r}
library("ggplot2")

graph1 <- qplot(terry$weight, terry$height,
      xlab = "Weights (kg)", ylab = "Heights (cm)",
      main = "Graph 2 showing Height measured against weight- Sample size -10 people",
      color = terry$sex, shape =terry$sex
)
graph2<- ggplot(data = terry, mapping = aes(weight, height, color = sex)) +
  geom_point(size= 7)+ scale_color_manual(breaks = c("Male", "Female"),values = c("red", "yellow"))
graph1
graph2
```

## Exercise 8.1
```{r}
data ("quakes")
write.table(x = quakes[quakes$mag >= 5,],file"C:/R-Studio/Finacials/q5.txt", sep = "!", row.names = FALSE)
q5dframe <- read.table(file = "C:/R- Studio/Finacials/q5.txt", sep = "!", header = TRUE)
q5dframe

library("car")
data("Duncan")
write.table(x = Duncan,file = "C:/R- Studio/Finacials/Duncan.txt", sep = "!", row.names = FALSE)
moreeighty <-  read.table(file = "C:/R- Studio/Finacials/Duncan.txt", sep = "!", header = TRUE)
moreeighty

library("ggplot2")

ggplot(data = moreeighty, mapping = aes(education, income),main ="Graph showing income against education") +
  geom_point(size= 3) + scale_color_manual(breaks = c(">=80", "=<80"),values = c("black", "white")+
  xlim(0, 100) +
  ggsave(filename = "C:/R- Studio/Finacials/car_duncan.png"))
##dev.off
tex <- list(quakes,q5dframe,Duncan)
tex
#(i) Writing Exercise8-1.txt list
#dput(file="C:/R- Studio/Finacials/Duncan.txt")
#(ii) Reading Exercise8_1.txt
list.of.dataframes <- dget("C:/R- Studio/Finacials/Duncan.txt")
list.of.dataframes
```
## Exercise 8.2
```{r}


## Exercise 9.1
```{r}
ls("package:methods")[1:20]
length(ls("package:methods"))

environment(read.table) ##utils
environment(data) ## Null
environment(matrix) ## base
environment(jpeg) ## grDevices

any(ls("package:graphics") == "smoothScatter")
```

## Excercise 9.2
```{r}
args(seq)
boz <- seq(-4,4,0.2)
boz

array(8:1, dim = c(2, 2, 2)) # using partital and positional argument stlye 
rep(1:2, 3) # positional arg stlye
seq(from = 10, to = 8, length = 5) # partital argument stlye
sort(decreasing = T, x = c(2, 1, 1, 2, 0.3, 3, 1.3)) # exact argument stlye
which(matrix(c(T, F, T, T), 2, 2)) # positional
which(matrix(c(T, F, T, T), 2, 2), a = T) #positional and mixed argument stlye

seeargs<- args(plot.default)
seeargs

plot.default(type = "p", pch = NULL, xlab = "years", ylab = "salary",
             lwd = NULL, lty = NULL, col = NULL,
             x = c(1, 5), y = c(10, 100))





```


















